\input{intro}
\input{relatedWork}
\input{functions}
\input{cloudnative}

\begin{comment}
\section{Enabling Technologies}
Extending Networking into the Virtualization Layer (see \cite{pfaff2009extending}) summarizes how the traditionally monolithic and physically bound domain of networking can be broken up and modularized by means of virtualization. The following three parts would focus on enabling and supporting technologies needed to realize the vision of this new paradigm. First, the business logic needs to be packaged and executed. This can happen in virtual machines, containers etc. Following that, virtualized switching technology needs to be put in place to allow for successful packet forwarding. One technology is Open vSwitch which is an implementation of a virtual switch, connecting virtual interfaces of VMs for instance with physical interfaces. Docker and Kubernetes additionally provide means for communication between several, executable artifacts.
\end{comment}


\quad




%\begin{description}
%	\item [VNF] Can complement the SDN paradigm (but can exist independently)  by providing functionality needed in the network domain as an executable artifact
%	\item [NFV] NFV integrates VNFs into a system that can manage and deploy these functions in sensible manner. 
%\end{description}

%\subsubsection{Organizations and Motivations}
%ETSI proposing NFV architecture already in 2012 in a white paper  \cite{nfv_wp}. The CNCF (Cloud-native Computing Foundation) has launched a testbed to compare the performance of VNFs on an OpenStack enviromnent versus a Kubernetes setup \footnote{https://www.cncf.io/announcement/2019/02/25/cncf-launches-cloud-native-network-functions-cnf-testbed/}	



\input{conclusion}

\begin{comment}
	

\section{List of references}
\begin{description}[style=sameline, leftmargin=1em, font=\normalfont]
	\item[Pfaff \cite{pfaff2009extending}]  Virtualization in Networking. Basics of how virtualization started to make its way into the networking domain. Overview of network architectures and topologies that employ virtualization. The starting of how to break up monoplithic network infrastructure with virtualization. The components decsribed here are the basis for VNFs (and the overarching NFV). 
	
	\item[Sherry \cite{sherry2016middleboxes}] Middleboxes as a Cloud Service. Traditional Network Functions are provided by specialized and proprietary middleboxes. What is their significance in 2016's enterprise and educational networks? The results of this paper motivate towards decoupling functionality from physical boxes and providing virtualized solutions.
	
	\item [Mijumbi \cite{mijumbi2016network}] NFV State of the art . Comprehensive overview of the state of the art of NFVs with focus on Telephony Service Providers. Interesting because critical evaluation of NFV solutions that, contrary to their original design, seem to result in a means to pool vendor specific resources together instead of supporting real interoperability. 
	
	\item [Bilal \cite{bilal2016impact}] Impact of CNFs . The authors analyze resource consumption of a real-life example, namely two different mobile networks and evaluate the impact virtualization would have on these networks. 
	
	\item [De Sousa \cite{de2019network}] Network Service Orchestration. The Network Service Orchestration is in the focus of this paper. The authors lay out a comprehensive survey over service orchestration technologies and additionally provide a taxonomy.  
	
	\item[NFV White Paper \cite{nfv_wp}]  The white paper lays out the foundation for NFV. 
	
	\item [AM White Paper \cite{evolutionnfv}] This white paper, seemingly sponsored by  Huawei, focuses on CNFs for telecommunication companies, including migration strategies from NFV to CNFs. 
	
	\item [CNF White Paper by Cisco \cite{CNF}] A white paper sponsored by Cisco provides insights into the point-of-view of a vendor. They set out to define what CNFs are, and how potential clients can benefit from them. They use Kubernetes as the main orchestrator and suggest it for further roles, too. 
	
	\item [Cloud-native 5G \cite{inproceedings}] The authors layout the implementation of VNFs that adhere to Cloud-native design principles for 5G. Furthermore they summarize existing projects and show an exemplary Use Case for this technology. Very relevant to my work, they use Docker for prototyping and are migrating to Kubernetes for the Cloud Native NFVI (Network Functions Virtualization Infrastructure) interface. A NFVI is specified here \cite{mijumbi2016network}.
	
	\todo{5G would also bring in an interesting perspective. You could show what kind of challenges are introduced with 5G for the network as well. }
	\todo{Reference/Specification for NFVI}
	
\end{description}

\end{comment}
